Selective stock enhancement undermines community stability

### 2022-01-22 rmd/supporting_info.Rmd
Update supporting_info.Rmd

@@

# Tables

```{r table_set1}

## load data for tables
source(here::here("code/table_reg.R"))

table_legend <- "Median estimates and standard errors (SEs) are shown. Pr(> 0) and Pr(< 0) represent the proportion of parameter estimates (MCMC samples) being positive and negative, respectively (i.e., posterior probability)."

table_reg <- NULL

@@

  if(name[i] == "all") {
    knit_chunk <- paste0("## Table S", i, " Parameter estimates for the regression model of whole community \n",
                         table_legend,
                         "\n```{r table_s", i,"}
                         \n\n
                         kable(df_est[[",i,"]], format = 'markdown')
                         \n\n
                         ```\n",
                         "\n\\pagebreak\n")
  }

  if(name[i] == "masu") {
    knit_chunk <- paste0("## Table S", i, " Parameter estimates for the regression model of masu salmon \n",
                         table_legend,
                         "\n```{r table_s", i,"}
                         \n\n
                         kable(df_est[[",i,"]], format = 'markdown')
                         \n\n
                         ```\n",
                         "\n\\pagebreak\n")
  }

  if(name[i] == "other") {
    knit_chunk <- paste0("## Table S", i, " Parameter estimates for the regression model of unenhanced species \n",
                         table_legend,
                         "\n```{r table_s", i,"}
                         \n\n
                         kable(df_est[[",i,"]], format = 'markdown')
                         \n\n```
                         \n",
                         "\n\\pagebreak\n")
  }

  table_reg <- c(table_reg, knit_chunk)
}

@@

`r paste(knit(text = table_reg), collapse = '\n')`

>>>>

```{=tex}
\newpage
\pagenumbering{arabic}
```
# Tables

## Table S1 Parameter values used in the main simulation
See Methods for model description.

```{r table_param_main_sim}

source(here::here("code/table_param_set.R"))
kable(df_param, format = "markdown")

@@

## Table S2 Parameter values used in the sensitivity analysis
In the sensitivity analysis, parameter values were randomly drawn from uniform distributions. Discrete parameters (number of species, carrying capacity) were rounded to the nearest integer prior to the analysis.

```{r table_param_stvy}

source(here::here("code/table_param_set.R"))
kable(df_param_stvy, format = "markdown")

```{r data_stvy, include=FALSE}

## load table for sensitivity analysis
source(here::here("code/table_stvy_analysis.R"))

```{r table_sensitivity, results="asis"}

j <- 2

## conditional text
c_text <- c("whole community",
            "enhanced species",
            "unenhanced species")

table_stvy_chunk <- knit_chunk <- NULL

for(i in 1:length(table_stvy)) {

  table_legend <- paste0("Sensitivity analysis of the community simulation. Parameter estimates of linear regression models (standard errors in parenthesis) are shown. Response variables are the effects of stock enhancement on temporal mean density ($\\mu$) and SD ($\\sigma$) of ", c_text[i],". Both response and explanatory variables (i.e., simulation parameters) were standardized to a mean of zero and a standard deviation of one prior to the analysis.")

  knit_chunk <- paste0("## Table S", i + j, " Sensitivity analysis (", c_text[i],") \n",
                       table_legend,
                       "\n```{r table_s", i + j,", results='asis'}
                       \n\n
                       cat(table_stvy[[", i,"]], sep = '\n')
                       \n\n
                       ```\n",
                       "\n\\pagebreak\n")

  table_stvy_chunk <- c(table_stvy_chunk, knit_chunk)

}

`r paste(knit(text = table_stvy_chunk), collapse = '\n')`

```{r table_reg}

j <- 5

## load regression tables
source(here::here("code/table_reg.R"))

## conditional text
c_text <- case_when(name == "all" ~ "whole community",
                    name == "masu" ~ "masu salmon",
                    name == "other" ~ "unenhanced species")

## common text
table_legend <- "Median estimates and standard errors (SEs) of regression coefficients are shown. Pr(> 0) and Pr(< 0) represent the proportion of positive and negative estimates (MCMC samples), respectively (i.e., posterior probability)."

table_reg_chunk <- knit_chunk <- NULL

@@

  knit_chunk <- paste0("## Table S", i + j, " Parameter estimates for the regression model of ", c_text[i], " \n",
                       table_legend,
                       "\n```{r table_s", i + j,"}
                       \n\n
                       kable(df_est[[",i,"]], format = 'markdown')
                       \n\n
                       ```\n",
                       "\n\\pagebreak\n")

  table_reg_chunk <- c(table_reg_chunk, knit_chunk)

}

@@

`r paste(knit(text = table_reg_chunk), collapse = '\n')`
